Embodied Neuromorphic Benchmarks

### 2015-08-26 paper/paper.tex
another typo

However, it is also clear that performance these benchmarks is a result of
a combination of the hardware itself, the algorithm being run, and the system that
interfaces the hardware to the environment.  Thus, for any given hardware, 
we can explore improvements to the algorithm (better choices for $e$, 
different learning rules, adaptive learning rates, adapting $K_p$ and $K_d$, etc.).
For example, in the SpiNNaker hardware implementation not only can the neuron model
be adjusted, but the distribution of the task across the multiple cores is also
under programmer control.  Furthermore, SpiNNaker provides a custom I/O interface
for high-speed communication that could be used to reduce communication delay.

>>>>

However, it is also clear that performance on these benchmarks is a result of
a combination of the hardware itself, the algorithm being run, and the system that
interfaces the hardware to the environment.  Thus, for any given hardware, 
we can explore improvements to the algorithm (better choices for $e$, 
different learning rules, adaptive learning rates, adapting $K_p$ and $K_d$, etc.).
For example, in the SpiNNaker hardware implementation not only can the neuron model
be adjusted, but the distribution of the task across the multiple cores is also
under programmer control.  Furthermore, SpiNNaker provides a custom I/O interface
for high-speed communication that could be used to reduce communication delay.
